Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-24 NEUROC/Response-MajRev/response_letter.tex

% R1Q5
\begin{point}
    In my view, computation efficiency is to describe the testing or validation process. Except for reporting and analyzing the training times, it is meaningful to discuss the inference time. This is also an important point of view for deep learning researchers to be concerned about.
\end{point}

\begin{reply}
    Thank you for the insightful comment and suggestion.
    %
    The efficiency of inference (including inference time and memory usage) is indeed important for deep learning researchers and engineers.
    %
    In the revised manuscript, we have added a new subsection (Section 2.5 ``Inference with GNNs'') in the revised manuscript to briefly review how to perform inference with GNNs.
    %
    To discuss the efficiency of GNN inference on GPUs, we have added performance bottleneck analysis on GNN inference in every subsection of Section 4 ``Evaluation Results and Analysis'':
    %
    \begin{enumerate}

        \item In Section 4.1 ``Effects of Hyper-parameters on Performance'', we have additionally measured how the inference time and the peak memory usage changed as we increased the values of the hyper-parameters.
        %
        We find that ...
        %%% TODO %%%

        \item In Section 4.2 ``Time Breakdown Analysis'', we have additionally conducted the time breakdown analysis for GNN inference.
        %
        We conducted the same set of experiments as in the training time anlaysis.
        %
        We found that the performance characteristics of GNN inference were very similar to GNN training.
        %
        The processing time breakdowns on the layer level, step level and operator level of training and inference were all highly similar, as shown in Figure~\ref{} of the response.
        %
        Based on the time breakdown analysis, we concluded that the performance bottenecks of GNN training and inference were same.
        %
        The difference between training and inference process was mainly reflected in the elapsed time.
        %
        Given the same dataset and the same GNN, the inference time was only XX\% of the training time, as compared in Figure~\ref{} of the response.
        %
        The training process of each epoch consisted of three phases: forward propagation, backward propagation and evaluation.
        %
        The evaluation phase conducted inference for the vertices in the evaluation set.
        %
        Under the semi-supervised learning setting, the graph neurons of the whole graph participated in inference, but only the labels of the veritces in the evaluation set were used to calculate accuracy.
        %
        Therefore, the elapsed time of the evaluation phase was very close to the elapsed time of inference.

### 2020-12-24 NEUROC/sec3-experiment-design.tex
更新R1Q5的回复。

We used six real-world graph datasets as listed in \tablename~\ref{tab:dataset_overview} that were popular in the GNN accuracy evaluation \cite{yang2016_revisiting_semisupervised, zeng2020_graphsaint, shchur2018_pitfall_of_gnn}.
%
For directed graphs, PyG converts them into undirected ones during data loading.
%
Thus, the average degree of a directed graph $\bar{d}=\frac{2|\mathcal{E}|}{|\mathcal{V}|}$.
%
For an undirected graph, the average degree is defined as $\bar{d}=\frac{|\mathcal{E}|}{|\mathcal{V}|}$.
%
For the \texttt{cam} dataset, since its vertices were not associated with feature vectors, we generated random dense feature vectors for it and excluded it from accuracy evaluation.
%
We also used random graphs generated by the R-MAT graph generator \cite{rmat-generator} in some experiments, to explore the effects of graph topological characteristics (like average degrees) on performance bottlenecks.
%
Input feature vectors of random graphs were random dense vectors with the dimension of 32.
%
Vertices of random graphs were classified into 10 classes randomly.

>>>>

We used six real-world graph datasets as listed in \tablename~\ref{tab:dataset_overview} that were popular in the GNN accuracy evaluation \cite{yang2016_revisiting_semisupervised, zeng2020_graphsaint, shchur2018_pitfall_of_gnn}.
%
For directed graphs, PyG converts them into undirected ones during data loading.
%
Thus, the average degree of a directed graph $\bar{d}=\frac{2|\mathcal{E}|}{|\mathcal{V}|}$.
%
For an undirected graph, the average degree is defined as $\bar{d}=\frac{|\mathcal{E}|}{|\mathcal{V}|}$.
%
For the \texttt{cam} dataset, since its vertices were not associated with feature vectors, we generated random dense feature vectors for it and excluded it from accuracy evaluation.
%
We also used random graphs generated by the R-MAT graph generator \cite{rmat-generator} in some experiments, to explore the effects of graph topological characteristics (like average degrees) on performance bottlenecks.
%
Input feature vectors of random graphs were random dense vectors with the dimension of 32.
%
Vertices of random graphs were classified into 10 classes randomly.
%
For \texttt{amp}, \texttt{amc}, \texttt{cph}, and \texttt{cam}, we used 70\%/15\%/15\% of the samples as the training/evaluation/test set, respectively.
%
For \texttt{pub}, we used 500/100 vertices as the evaluation/test set and the remained as the training set according to X.
%
For \texttt{fli}, we used 50\%/25\%/25\% of the samples as the training/evaluation/test set according to X.
